First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/body.tex
update

An electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
by the SHMS ans High Momentum Spectrometer (HMS), respectivly. The ``missing'' (undetected) neutron was reconstructed from momentum conservation laws.

@@

\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes (scintillator arrays) used for triggering,
2) a pair of drift chambers used for tracking, 3) a calorimeter used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}erenkov used also for $e^{-}/\pi^{-}$ and an additional
Noble Gas \u{C}erenkov used in the SHMS for $e^{-}/\pi^{+}/K^{+}$ at momenta $>$ 6 GeV/c. Due to the absence of significant background on this experiment and the low coincidence trigger rates

@@

multiple times resulting in either the spectrometer angle or momentum not being excactly the same. As a result, two separate data sets measured for the 580 MeV/c and three data sets for the 750 MeV/c setting.  
The spectrometer central settings are approximately as follows: the SHMS central angle and momentum settings were kept fixed at (12.194 deg, 8.5342 GeV/c) and the HMS central angle and momentum settings were changed from
(38.896 deg, 2.840 GeV/c) at the 80 MeV setting to (54.992 deg, 2.1925 GeV/c) and (58.391 deg, 2.0915 GeV/c) at the 580 and 750 MeV/c settings, respectively. At these kinematics, the
3-momentum transfer is $|\vec{q}| = 2.86$ GeV/c and is on the order of the final proton momentum indicating that most of the energy and momentum are transferred to the proton. As a result, the ejected proton
scatters at angles $\theta_{pq}\sim 0$, relative to the $\vec{q}$. This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the neutron is struck and the proton is a spectator. \\

@@

simulation program, \texttt{SIMC}. Additional $^{1}H(e,e'p)$ data was also taken at three other kinematic settings that covered the entire SHMS momentum acceptance range and were used for spectrometer optics studies and
calibration. \\

@@

is well known, 2) an HMS collimator cut to restrict the spectrometer solid angle acceptance to events that only passed through the collimator and not by re-scattering from the edges, 3) a missing
energy cut (peak $\sim$ 2.2 MeV for the deuteron) to select true $ep$ coincidences and not events from the radiative tail, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the

@@

\indent The experimental data yield was normalized by the total charge and corrected for tracking efficiencies, total live time, proton absorption and target boiling factors.

@@

of up to $\sim 20 \%$ for recoil momenta up to $\sim$ 250 MeV/c were observed which are typical for this setting using the Paris potential. The 80 MeV data was also checked for reproducibility against the Hall A data.

@@

\indent The systematic uncertainties on the measured cross sections were determined from 1) normalization and 2) kinematic uncertainties. The individual contributions from normalization uncertainties

@@

The theoretical calculations used in the bin-centering corrections were done by J.M. Laget using the Paris potential. \\
\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data of set independently and were averaged for overlapping bins in $p_{r}$,

@@

where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated from P. Bosted's form factor parametrization \cite{PhysRevC.51.409}.
Only within the PWIA, $\sigma_{red}$ can be interpreted as the proton momentum distribution inside the deuteron where most of the kinematical dependencies that arise from the

@@

\includegraphics[scale=0.5]{prl_plots/PRL_plot2.pdf}

@@

to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn) potential is shown in Fig. \ref{fig:fig1}. The theoretical calculations for the
CD-Bonn and Argonne $v_{18}$ (AV18) potentials were performed by M. Sargsian and those for the Paris potential were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is

@@

CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn curves, whereas the data shows

@@

provides a continutity to the data from this experiment in the transition region from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there was no data. There is also an overall good agreement between the two experiments
in the regions in which they overlap in $p_{r}$. \\

@@

characteristic ``flattening'' (smaller falloff) with $p_{r}$. This behaviour of FSI with larger recoil angles was predicted by the GEA and was first verified by the Hall A experiment.

@@

\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig2]{2(a)}] and  \hyperref[fig:fig2]{2(b)}],  all models predict similar behaviour of the momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$,
however, the momentum distributions become increasingly sensitive to the NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
\indent In Fig. \hyperref[fig:fig2]{2(a)} for example, the data clearly favors the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models.
For recoil angles in Fig. \hyperref[fig:fig2]{2(b)}, a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$
as opposed to Fig. \hyperref[fig:fig2]{2(a)}. For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.

@@

\begin{figure}[bh!]
\includegraphics[scale=0.5]{prl_plots/PRL_plot1.pdf}
\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles \\  $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
\label{fig:fig2}
\end{figure}

\twocolumngrid
\indent We have measured the

>>>>

A 10.6005 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
by the SHMS and High Momentum Spectrometer (HMS), respectivly. The ``missing'' (undetected) neutron was reconstructed from momentum conservation laws.

@@

\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes\cite{hodo_techreport} (scintillator arrays) used for triggering,
2) a pair of drift chambers\cite{dc_techreport} used for tracking, 3) a calorimeter\cite{Mkrtchyan_2013} used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used also for $e^{-}/\pi^{-}$ separation.
Due to the absence of significant background on this experiment and the low coincidence trigger rates

@@

multiple times resulting in either the spectrometer angle or momentum not being excactly the same. As a result, two separate data sets were measured for the 580 MeV/c setting and three data sets for the 750 MeV/c setting.  
The spectrometer central settings are approximately as follows: the SHMS central angle and momentum settings were kept ``fixed'' at ($\sim$12.194 deg, 8.5342 GeV/c) and the HMS central angle and momentum settings were changed from
(38.896 deg, 2.840 GeV/c) at the 80 MeV setting to $\sim$(54.992 deg, 2.1925 GeV/c) and $\sim$(58.391 deg, 2.0915 GeV/c) at the 580 and 750 MeV/c settings, respectively. \\
\indent At these kinematics, the 3-momentum transfer is $|\vec{q}| \sim 2.88$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$) measured on this experiment. As a result
one can infer that most of the virtual photon momentum is transferred to the proton. This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the
neutron is struck while the detected proton is a spectator. FSIs are also expected to be largely reduced as compared to the ``perpendicular-kinematics'' in which the
proton is detected almost perpendicular to $\vec{q}$ based on a calculation by Arenh\"{o}vel on Table 1 of Ref.\cite{pr01-020}.\\
% (5) At these kinematics, the 3-momentum transfer is $|\vec{q}| = 2.86$ GeV/c and is on the order of the final proton momentum indicating that most of the energy and momentum are transferred
%to the proton. As a result, the ejected proton scatters at angles $\theta_{pq}\sim 0$, relative to the $\vec{q}$. This configuration is known as the ``parallel-kinematics'' and suppresses
%the process in which the neutron is struck and the proton is a spectator. \\

@@

simulation program, SIMC. Additional $^{1}H(e,e'p)$ data was also taken at three other kinematic settings that covered the entire SHMS momentum acceptance range and were used for spectrometer optics optimization, 
momentum calibration and determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}. \\

@@

is well known, 2) an HMS collimator cut to restrict the spectrometer solid angle acceptance to events that only passed through the collimator and not by re-scattering from the collimator edges, 3) a missing
energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $ep$ coincidences and not events from the radiative tail, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the

@@

\indent The experimental data yield was normalized by the total charge and corrected for tracking efficiencies, total live time, proton absorption\cite{cyero_pAbs} and target boiling factors\cite{cyero_tgtBoil}.

@@

of up to $\sim 20 \%$ for recoil momenta up to $\sim$ 250 MeV/c were observed which are typical for this setting using the Paris potential. The 80 MeV data was also checked for reproducibility against the Hall A data (See Fig. \ref{fig:fig2}).

@@

\indent The systematic uncertainties on the measured cross sections were determined from normalization\footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made. Determination of systematics on these quantities is a work in progress. (Private communication with D. Mack)} and kinematic uncertainties. The individual contributions from normalization uncertainties

@@

The theoretical calculations used in the bin-centering corrections were done by J.M. Laget using the Paris potential\cite{PhysRevC.21.861}. \\
\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were averaged for overlapping bins in $p_{r}$,

@@

where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated using P. Bosted's form factor parametrization \cite{PhysRevC.51.409}.
Only within the PWIA, can $\sigma_{red}$ be interpreted as the proton momentum distribution inside the deuteron where most of the kinematical dependencies that arise from the

@@

\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}

@@

relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig1}. The theoretical calculations for the
CD-Bonn and Argonne $v_{18}$\cite{PhysRevC.51.38} (AV18) potentials were performed by M. Sargsian and those for the Paris potential were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is

@@

CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn, whereas the data shows

@@

provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\

@@

smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions. This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{PhysRevC.56.1124,Sargsian_2001} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.

@@

\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig2]{2(a)} and  \hyperref[fig:fig2]{2(b)},  all models predict similar behaviour of the
momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
\indent In Fig. \hyperref[fig:fig2]{2(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig2]{2(b)},
a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start 

@@

\begin{center}
\begin{figure}[hb!]
\includegraphics[scale=0.5]{../prl_plots/PRL_plot1.pdf}
\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
\label{fig:fig2}
\end{center} \\
%Begin text ON NEW PAGE after FIGURE 2. If Figure 2 changed position, move text from previous page (top) to this page (bottom)
\twocolumngrid
\noindent to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig2]{2(a)}.
For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\
\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhances the high momentum components of the deuteron wavefunctions.
%while suppressing long-range processes such as MECs or ICs. FSIs have also been largely suppressed by selecting a kinematic window found in the previous Hall A 
%experiment where FSIs were found to be reduced and independent of missing momentum at recoil angles $35^{o}\leq\theta_{nq}\leq45^{o}$. This experiment took advantage
%of that kinematic window and extended the cross section measurements beyond $p_{r}\sim$500 MeV/c.
The experimental reduced cross sections were extracted and found to be best described by the CD-Bonn potential with sensitivity to the CD-Bonn momentum distributions
up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
behavior that was not predicted by any of the models. \\
\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days) of beam time and 3 out of the 8 kinematic settings approved in
the original proposal\cite{e12_10_003_proposal}, we conclude that the results presented on this Letter (although very interesting) do not have the
necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed.
It would be highly desireable to perform the full experiment

%We conclude that these results although very interesting, does not have the sufficient statistics and the
%required number of high missing momentum settings to make a definitive argument about the underlying physics observed.\\

%high momentum components of the deuteron wavefunction by suppressing other reaction mechanisms such as MECs or ICs

### 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/prl.tex
update

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version xx as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
\centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
  neutron recoil momenta up to 1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the neutron recoil
  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and comparison
  to recent theoretical calculations show data to be sensitive to momentum distributions up to $\sim$ 700 MeV/c recoil momenta.

@@

\input introduction.tex
\input body.tex
%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\   %This space must remain here to keep the acknowledgemn section in place
\input acknowledgement.tex   % input acknowledgement
\bibliography{prl}

\end{document}
%
% ****** End of file template.aps ******

>>>>

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 00 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
\centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 GeV$^{2}$ and
  neutron recoil momenta up to $p_{r}\sim$1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the in-plane neutron recoil
  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA)
  dominates and comparison to recent theoretical calculations show data to be sensitive to momentum distributions up to $p_{r}\sim$ 700 MeV/c.

@@

\input introduction.tex
\input body.tex
\input acknowledgement.tex    % input acknowledgement
\bibliography{prl}
.\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\end{document}
%
% ****** End of file template.aps ******

### 2019-11-14 MY_PUBLICATIONS/PRL/pre_draft/body.tex
update

\begin{figure}[bh!]
\includegraphics[scale=0.5]{prl_plots/PRL_plot1.pdf}
\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles \\  $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
\label{fig:fig2}
\end{figure}

\twocolumngrid
\indent We have measured the

>>>>

\begin{figure}[bh!]
\includegraphics[scale=0.5]{../prl_plots/PRL_plot1.pdf}
\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles \\  $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
\label{fig:fig2}
\end{figure}

\twocolumngrid
\indent In summary, this commissioning experiment extends the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhances the high momentum components of the deuteron wavefunctions
while suppressing long-range processes such as MECs or ICs. FSIs have also been largely suppressed by selecting a kinematic window found in the previous Hall A 
experiment where FSIs were found to be reduced and independent of missing momentum at recoil angles $35^{o}\leq\theta_{nq}\leq45^{o}$. This experiment took advantage
of that kinematic window and extended the cross section measurements beyond $p_{r}\sim$500 MeV/c. The experimental reduced cross sections were extracted and found to
be best described by the CD-Bonn potential with sensitivity to the CD-Bonn momentum distributions up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$,
respectively before the data transitioning to other theoretical models, which is a behavior that was not predicted by any of the models. We conclude that these results although
very interesting, does not have the sufficient statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed.

%high momentum components of the deuteron wavefunction by suppressing other reaction mechanisms such as MECs or ICs

### 2019-11-14 MY_PUBLICATIONS/PRL/pre_draft/introduction.tex
update

nucleon pair begins to overlap. The overlap is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}. Short-distance studies
of the deuteron are also important in determining whether or to what extent the description of nuclei in terms of nucleon/meson degrees of freedom must be supplemented
by the inclusion of explicit quark effects, which is an issue of fundamental importance in nuclear physics\cite{pr01-020}. To date, there are only a few nuclear experiments for
which a transition between nucleonic to quark degrees of freedom can be observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}. This Letter presents
first results of $^{2}H(e,e'p)n$ in which kinematics were taken to the limit where a transition to non-nucleoninc degrees of freedom is expected.\\

>>>>

nucleon pair begins to overlap. The overlap is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}.
Short-range studies of the deuteron are also important in determining whether or to what extent can nuclei be described in terms of nucleon/meson degrees of freedom before
having to include explicit quark effects, which is an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
This Letter presents first results of $^{2}H(e,e'p)n$ in which kinematics were taken to the limit where a transition to non-nucleoninc degrees of freedom is expected.\\
